---
title: "Rdata, Rda, Rds 数据的存储和导入"
date: '2020-12-16'
output: 
  html_document:
    
  md_document:
    variant: markdown_github
  
    
---

`bibliometrix` 使用 `load()` 函数来读取 R 数据，读取 `*.Rds` 时会出错。

问题和解答来自这里：
https://stackoverflow.com/questions/21370132/r-data-formats-rdata-rda-rds-etc

**问题**

> What are the main differences between .RData, .Rda and .Rds files?
>
> More specifically:
> 
> Are there differences in compression etc?
> When should each type be used?
> How to convert one type to another?


**解答**

`Rda` is just a short name for `RData`. You can just `save()`, `load()`, `attach()`, etc. just like you do with RData.

`Rds` stores a single R object. Yet, beyond that simple explanation, there are several differences from a "standard" storage. Probably this R-manual Link to `readRDS()` function clarifies such distinctions sufficiently.

So, answering your questions:

The difference is not about the compression, but serialization (See this page)
Like shown in the manual page, you may wanna use it to restore a certain object with a different name, for instance.
You may `readRDS()` and `save()`, or `load()` and `saveRDS()` selectively.

下面是几个例子。

先分别保存一个数据到 `rda` 和 `rds` 格式（两个语句语法有差异）。

```{r}
# create a data d, and save it
d <- 1:5
e <- 8
save(d, file = "rda.Rda")
save.image(file = "image.RData")
saveRDS(d, file = "rds.rds")
rm(d,e)
```

然后再读取他们。

首先 `load()`，`load()` 直接将原来的变量导入，而变量的名称则被其当做返回值赋值给了 `a`。

```{r}
a <- load("rda.rda")
```

`load()` 可以载入单个变量，也可以载入多个变量。


```{r}
a
d
```


如果想把 load() 的变量改个名字，则可以这样操作。

```{r}
eval(parse(text = paste0("c <- ",a)))
c
```

```{r}
rm(list=ls())
```

```{r}
a <- load("image.RData")
a
d
e
```

这时候如果还想要通过上面的方法改变变量的名称，那就有问题了。

```{r}
(cmd <- parse(text = paste0("c <- ",a)))
eval(cmd)
c
```

在多次赋值后，最后一个值被赋给了 `c` 变量，同时没有任何提示。


```{r}
rm(list=ls())
```
如果是一个空的环境的话，保存后会出现什么情况呢？

```{r}
save.image(file = "empty.RData")
a <- load("empty.RData")
a
```


其次看 `readRDS()`, 它将变量的值赋给了 `c`。

```{r}
c <- readRDS("rds.rds")
c
rm(c)
```
使用 `load()` 读取 `.rds` 数据会出错。

```{r error=TRUE}
load("rds.rds")
```

