---
title: "rlang 中与参数相关的特殊操作符"
date: "2021-1-8"
---

## 奇妙的引用 - Quoting/defusing

> The defusing operators `expr()` and `enquo()` prevent the evaluation of R code. **Defusing** is also known as **quoting**, and is done in base R by `quote()` and `substitute()`. When a function argument is defused, R doesn't return its value like it normally would but it returns the R expression describing how to make the value. These defused expressions are like blueprints for computing values. Source: <https://rlang.r-lib.org/reference/nse-defuse.html>

引用可以避免 R 代码被解释和执行，但是仍然可以使用强制执行函数解释其内部的代码。

```{r}
# All these quoting functions have quasiquotation support. This
# means that you can unquote (evaluate and inline) part of the
# captured expression:
what <- sym("bonjour")
expr(say(what))
#> say(what)
expr(say(!!what))
#> say(bonjour)

```

## 强制执行操作符

`!!` 和 `!!!` 是 `rlang` 中定义的前缀操作符。`!!()` = `UQ()`, `!!!()` = `UQS()`。 不过，`UQ()` 函数目前已经逐渐不再使用，未来推荐使用 `!!()`。

```{r}
# Bad
rlang::expr(mean(rlang::UQ(var) * 100))

# Ok
rlang::expr(mean(UQ(var) * 100))

# Good
rlang::expr(mean(!!var * 100))
```

`!!` 用来去掉参数的引号。

```{r}
library(tidyverse)
x <- expr(a+b+c)
x
expr(f(!!x,y))
```

```{r}
var <- "x"
val <- c(4, 3, 9)

tibble(!!var := val)
#> # A tibble: 3 x 1
#>       x
#>   <dbl>
#> 1     4
#> 2     3
#> 3     9
```

`!!` 常用的一个情况是访问 `data.frame` 中的一个变量。

```{r}
# The environment variable `var` refers to the data-variable
# `height`
var <- sym("height")

# We force `var`, which substitutes it with `height`
starwars %>%
  summarise(avg = mean(!!var, na.rm = TRUE))
```

这相当于执行了下面的操作。

```{r}
starwars %>%
  summarise(avg = mean(height, na.rm = TRUE))
```

`!!!`用来去掉**多个**参数的引号。

```{r}
vars <- syms(c("height", "mass"))

# Force-splicing is equivalent to supplying the elements separately
starwars %>% select(!!!vars)
starwars %>% select(height, mass)
```

> 之所以引入新的 `:=` 赋值操作符是因为`=`不接受表达式（expression）作为参数的名称。`:=` 在此处的作用与 `=` 类似，但是更灵活。

## 双大括号

这个情况比较特殊，通常是在处理函数的参数时被使用。

```{r}
# Force-defuse all function arguments that might contain
# data-variables by embracing them with {{ }}
mean_by <- function(data, by, var) {
  data %>%
    group_by({{ by }}) %>%
    summarise(avg = mean({{ var }}, na.rm = TRUE))
}

# The env-variables `by` and `var` are forced but defused.
# The data-variables they contain are evaluated by dplyr later on
# in data context.
iris %>% mean_by(by = Species, var = Sepal.Width)

```

更多内容参考:

-   <https://adv-r.hadley.nz/quasiquotation.html>
-   <https://rlang.r-lib.org/reference/nse-force.html>
